Blum axioms and nondeterministic computation of functions

### 2016-04-17 paper.tex
paper.tex: Rearrange footnotes in the end of the section about Hopcroft-Ullman's definition.

But nondeterministic deciders,
although computationally equivalent to deterministic ones,
are apparently exponentially faster.
That is, while we have linear-time non-deterministic algorithms for Boolean satisfiability,
the best known deterministic algorithms are still exponential in the worst case.
Nondeterminism seems special in this sense;
although other extensions (multiple tapes and doubly-infinite tapes)
can be simulated under just a polynomial slowdown,
the simulation of nondeterminism seems to require exponential slowdown.%
\footnote{
    Simulating nondeterminism under a polynomial slowdown would show that $\P = \NP$;
    showing that the slowdown must be exponential would show that $\P \neq \NP$.
    Although most researchers expect the later to be the case~\cite[p.~54]{Gasarch2012},
    as Papadimitriou noted~\cite[p.~412]{Papadimitriou1994},
    in the absence of a proof that $\P \neq \NP$
    we should not be too emphatic in stating the simulation \emph{require}
    (as opposed to \emph{seemingly require}) exponential slowdown.
}
Therefore,
our definition must exhibit this apparent exponential speedup
when computing, for instance, the characteristic function of $\SAT$.
This is the ``non-deterministic'' part.

@@

We can try to fix this definition by forcing all branches to halt;
but then, as all branches are required to return the same value,
the machine will be (almost) deterministic.
Therefore, if there is a machine $M$ that computes the characteristic function%
\footnote{
    The characteristic function of a set $A \subseteq \Sigma^*$
    is the function $f$ defined by
    \begin{equation*}
        f(x) = \begin{cases}
            1, & \text{if $x \in A$}. \\
            0, & \text{if $x \notin A$}.
        \end{cases}
    \end{equation*}
}
of the satisfiability problem in nondeterministic polynomial time,
we could simulate $M$ on a given input,
choosing (say) always the first option when confronted with nondeterminism.
If this branch of computation returns $1$,
then every branch returns $1$ and the input is satisfiable;
if this branch returns $0$, every branch returns $0$ and the input is unsatisfiable.
We thus could solve $\SAT$ in \emph{deterministic} polynomial time.

Therefore, with this restriction,
we lose the apparent exponential speed up in computation time%
\footnote{
    It is ``apparent'' in the sense that,
    if $\P \neq \NP$,
    we will have this exponential slowdown in some problems
    when moving from nondeterministic to deterministic machines.
}
we have when using nondeterminism.
We thus will analyze the following models
to see whether they also suffer from this problem.

>>>>

But nondeterministic deciders,
although computationally equivalent to deterministic ones,
are apparently exponentially faster.
That is, while we have linear-time non-deterministic algorithms for Boolean satisfiability,
the best known deterministic algorithms are still exponential in the worst case.
Nondeterminism seems special in this sense;
although other extensions (multiple tapes and doubly-infinite tapes)
can be simulated under just a polynomial slowdown,
the simulation of nondeterminism seems to require exponential slowdown.%
\footnote{
    Simulating nondeterminism under a polynomial slowdown would show that $\P = \NP$;
    showing that the slowdown must be exponential would show that $\P \neq \NP$.
    Although most researchers expect the later to be the case~\cite[p.~54]{Gasarch2012},
    as Papadimitriou noted~\cite[p.~412]{Papadimitriou1994},
    in the absence of a proof that $\P \neq \NP$
    we should not be too emphatic in stating the simulation \emph{require}
    (as opposed to \emph{seemingly require}) exponential slowdown.
}
Therefore,
our definition must exhibit this apparent exponential speedup
when computing, for instance, the characteristic function\footnotemark{} of $\SAT$.
\footnotetext{
    The characteristic function of a set $A \subseteq \Sigma^*$
    is the function $f$ defined by
    \begin{equation*}
        f(x) = \begin{cases}
            1, & \text{if $x \in A$}. \\
            0, & \text{if $x \notin A$}.
        \end{cases}
    \end{equation*}
}
This is the ``non-deterministic'' part.

@@

We can try to fix this definition by forcing all branches to halt;
but then, as all branches are required to return the same value,
the machine will be (almost) deterministic.
Therefore, if there is a machine $M$ that computes the characteristic function
of the satisfiability problem in nondeterministic polynomial time,
we could simulate $M$ on a given input,
choosing (say) always the first option when confronted with nondeterminism.
If this branch of computation returns $1$,
then every branch returns $1$ and the input is satisfiable;
if this branch returns $0$, every branch returns $0$ and the input is unsatisfiable.
We thus could solve $\SAT$ in \emph{deterministic} polynomial time.

Therefore, with this restriction,
we lose the apparent exponential speed up in computation time
we have when using nondeterminism.
We thus will analyze the following models
to see whether they also suffer from this problem.
